Abstractions for Type-Level Programming

### 2022-05-27 public.tex
Add pictures
update slides
Fix typo

\usepackage{textpos}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{ulem}

@@

@@

\begin{slide}{Type-level programming: regular expression example}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}llrrr@{}}
\toprule
|input| & |pattern| & |out[0]| & |out[1]| & |out[2]| \\
\midrule
|"17:00"| & |"(\d+)[.:h](\d+)"| & |"17"| & |"00"|  & \\
\pause
|"25.05.2022"| & |"(\d+).(\d+).(\d+)"| & |"25"| & |"05"| & |"2022"| \\
\bottomrule
\end{tabular}
\end{center}
\end{slide}

\begin{slide}{Type-level programming: regular expression example}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}llrrr@{}}
\toprule
|input| & |pattern| & |out[0]| & |out[1]| & |out[2]| \\
\midrule
|"17:00"| & |"(\d+)[.:h](\d+)"| & |"17"| & |"00"|  & \cross \\
|"25.05.2022"| & |"(\d+).(\d+).(\d+)"| & |"25"| & |"05"| & |"2022"| \\
\bottomrule
\end{tabular}
\end{center}
\end{slide}

@@

\begin{slide}{Conclusion}
\Large
In this talk, I presented an analogy to explain what we do in the \sout{Programming} Poetry Methods Laboratory.

I also presented a few example to illustate my contribution:

\begin{center}
  \includegraphics[width=0.25\textwidth]{figures/poetry.jpg}
  \hspace{10pt}
  \includegraphics[width=0.32\textwidth]{figures/cards.png}
  \hspace{10pt}
  \includegraphics[width=0.25\textwidth]{figures/cff-logo.jpg}
\end{center}

\end{slide}

>>>>

\usepackage{textpos}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{booktabs}

@@

\begin{center}
\hspace{20pt}
\begin{minipage}{0.45\textwidth}%
\phantom{-- en alexandrin}\\
Roses are red,\\
violets are blue,\\
so are you. \checkmark
\end{minipage}
\end{center}
\end{slide}

@@

\begin{slide}{Type-level programming: regular expression example}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}llrrr@{}}
\toprule
|input| & |pattern| & |out[0]| & |out[1]| & |out[2]| \\
\midrule
|"17:00"| & |"(\d+)[.:h](\d+)"| & |"17"| & |"00"|  & \\
\pause
|"25.05.2022"| & |"(\d+).(\d+).(\d+)"| & |"25"| & |"05"| & |"2022"| \\
\bottomrule
\end{tabular}

\phantom{\includegraphics[width=0.92\textwidth]{figures/error2.png}}
\end{center}
\end{slide}

\begin{slide}{Type-level programming: regular expression example}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}llrrr@{}}
\toprule
|input| & |pattern| & |out[0]| & |out[1]| & |out[2]| \\
\midrule
|"17:00"| & |"(\d+)[.:h](\d+)"| & |"17"| & |"00"|  & \cross \\
|"25.05.2022"| & |"(\d+).(\d+).(\d+)"| & |"25"| & |"05"| & |"2022"| \\
\bottomrule
\end{tabular}

\phantom{\includegraphics[width=0.92\textwidth]{figures/error2.png}}
\end{center}
\end{slide}

\begin{slide}{Type-level programming: regular expression example}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}llrrr@{}}
\toprule
|input| & |pattern| & |out[0]| & |out[1]| & |out[2]| \\
\midrule
|"17:00"| & |"(\d+)[.:h](\d+)"| & |"17"| & |"00"|  & \cross \\
|"25.05.2022"| & |"(\d+).(\d+).(\d+)"| & |"25"| & |"05"| & |"2022"| \\
\bottomrule
\end{tabular}

\includegraphics[width=0.92\textwidth]{figures/error2.png}
\end{center}
\end{slide}

@@

\begin{slide}{Conclusion}
\Large
In this talk, I presented an analogy to explain what we do in the Poetry Methods Laboratory.

I also presented a few examples to illustate my contribution:

\begin{center}
  \includegraphics[width=0.25\textwidth]{figures/poetry.jpg}
  \hspace{10pt}
  \includegraphics[width=0.32\textwidth]{figures/cards.png}
  \hspace{10pt}
  \includegraphics[width=0.25\textwidth]{figures/cff-logo.jpg}
\end{center}
\end{slide}

\section{Acknowledgments}

\begin{slide}{Martin}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/martin.jpg}
\end{center}
\end{slide}

\begin{slide}{LAMP, LARA \& Scala Center}
\begin{center}
\includegraphics[width=\textwidth]{figures/ski-trip.jpg}
\end{center}
\end{slide}

\begin{slide}{Georg \& Mia}
\begin{center}
\includegraphics[width=\textwidth]{figures/bike-trip.jpg}
\end{center}
\end{slide}

\begin{slide}{Alicia \& Leila}
\begin{center}
\includegraphics[width=0.7\textwidth]{figures/alicia-2.png}
\end{center}
\end{slide}

\begin{slide}{Sol, Christian \& Leila}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/parents.jpg}
\end{center}
\end{slide}

\begin{slide}{Dragana \& Leila}
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/dragana.jpg}
\end{center}
\end{slide}
